---
title: "Next Day Stocks Movement"
author: "Sai Teja Reddy"
date: "05/03/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 
library(quantmod) 
library(dplyr)
library(bizdays)
library(caret)

cal <- create.calendar("Asia/Kolkata", holidaysANBIMA, weekdays=c("saturday", "sunday"))
next_working_day = following(Sys.Date(), cal)

nse_data <- read.csv(paste0(getwd(),"/data/Nifty50_Stocks.csv"))

final_technical_data <- data.frame("Stock"=character(0),"Pivot Point"=numeric(0),"Classical R3"=numeric(0),"Classical R2"=numeric(0),"Classical R1"=numeric(0),"Classical S1"=numeric(0),"Classical S2"=numeric(0),"Classical S3"=numeric(0),"Fibonacci R3"=numeric(0),"Fibonacci R2"=numeric(0),"Fibonacci R1"=numeric(0),"Fibonacci S1"=numeric(0),"Fibonacci S2"=numeric(0),"Fibonacci S3"=numeric(0))

for(i in 1:nrow(nse_data)){
  stock = nse_data[i,2]

  stock_data <- getSymbols(stock,src = "yahoo" , from = "2020-07-01", to = Sys.Date(),periodicity = "daily", auto.assign = FALSE)
  stock_data <- data.frame(Date = index(stock_data), coredata(stock_data) )
  names(stock_data) <- c("dates", "Open", "High", "Low", "Close", "Volume", "Adjusted")
  
  df <- tail(stock_data,1)
  
  pivot_point = (df$High + df$Low + df$Close)/3
  
  support_1 = round((2*pivot_point) - df$High,2)
  
  resistance_1 = round((2*pivot_point) - df$Low,2)
  
  support_2 = round(pivot_point - (resistance_1 - support_1),2)
  
  resistance_2 = round((pivot_point - support_1 ) + resistance_1,2)
  
  resistance_3 = round((pivot_point - support_2 ) + resistance_2,2)
  
  support_3 = round(pivot_point - (resistance_2 - support_2),2)
  
  Pivot_levels <-data.frame()
  
  Pivot_levels <- rbind(Pivot_levels, c(stock,round(pivot_point,2),resistance_3,resistance_2,resistance_1,support_1,support_2,support_3))
  
  colnames(Pivot_levels) = c("Stock","Pivot Point","Classical R3","Classical R2","Classical R1","Classical S1","Classical S2","Classical S3")
  
  
  price_difference = (df$High - df$Low)
  
  R1 = round((23.6*price_difference/100) + pivot_point,2)
  
  R2 = round((38.2*price_difference/100) + pivot_point,2)
  
  R3 = round((50*price_difference/100) + pivot_point,2)
  
  R4 = round((61.8*price_difference/100) + pivot_point,2)
  
  R5 = round((100*price_difference/100) + pivot_point,2)
  
  S1 = round(pivot_point - (23.6*price_difference/100),2)
  
  S2 = round(pivot_point - (38.2*price_difference/100),2)
  
  S3 = round(pivot_point - (50*price_difference/100),2)
  
  S4 = round(pivot_point - (61.8*price_difference/100),2)
  
  S5 = round(pivot_point - (100*price_difference/100),2)
  
  Fibonacci_levels <-data.frame()
  
  Fibonacci_levels <- rbind(Fibonacci_levels, c(R5,R4,R2,S2,S4,S5))
  
  colnames(Fibonacci_levels) = c("Fibonacci R3","Fibonacci R2","Fibonacci R1","Fibonacci S1","Fibonacci S2","Fibonacci S3")
  
  temp_technicals <- cbind(Pivot_levels,Fibonacci_levels)
  
  final_technical_data <- rbind(final_technical_data,temp_technicals)
}


increment = 1

final_levels_df = data.frame("Stock" = character(0),"Rider_Bullish" = character(0),"Bullish_Level"=character(0),"Rider_Bearish"=character(0),"Bearish_Level"=character(0))

logistic_prediction <- data.frame("Stock"=character(0),"Direction"=character(0))

for(i in 1:nrow(nse_data)){
  stock = nse_data[i,2]
  today = Sys.Date()
  f <- function(d)if(format(d - 1, '%w') %in% c(0, 5)) Recall(d - 1) else d
  previousWorkingDay <- f(today)

  print(stock)

  stocks_data <- na.omit(getSymbols(stock, src = "yahoo", from = "2008-01-01", to = Sys.Date()+1, auto.assign = FALSE))

  stocks_data2 <- stocks_data

  ichimoku <- function(HLC, nFast=9, nMed=26, nSlow=52) {
    turningLine <- (runMax(Hi(HLC), nFast)+runMin(Lo(HLC), nFast))/2
    baseLine <- (runMax(Hi(HLC), nMed)+runMin(Lo(HLC), nMed))/2

    out = cbind(turningLine,baseLine)
    return(out)
  }
  # browser()


  myATR <- function(x) ATR(HLC(x))[,'atr'] # Average True Range, measures volatility of series
  mySMI <- function(x) SMI(HLC(x))[, "SMI"] #  Stochastic Momentum Index
  myADX <- function(x) ADX(HLC(x))[,'ADX'] # Welles Wilder's Directional Movement Index
  myAroon <- function(x) aroon(cbind(Hi(x),Lo(x)))$oscillator # Identify starting trends
  myBB <- function(x) BBands(HLC(x))[, "pctB"] # Bollinger Bands
  myChaikinVol <- function(x) Delt(chaikinVolatility(cbind(Hi(x),Lo(x))))[, 1] # Chaikin Volatility
  myCLV <- function(x) EMA(CLV(HLC(x)))[, 1] # Close Location Value
  myEMV <- function(x) EMV(cbind(Hi(x),Lo(x)),Vo(x))[,2] # Arms' Ease of Movement Value
  myMACD <- function(x) MACD(Cl(x))[,2] # Moving Average Convergence Divergence
  myMFI <- function(x) MFI(HLC(x), Vo(x)) # Money Flow Index
  mySAR <- function(x) SAR(cbind(Hi(x),Cl(x))) [,1] # Parabolic Stop-and-Reverse
  myVolat <- function(x) volatility(OHLC(x),calc="garman")[,1] # volatility

  stocks_data$ATR <- myATR(stocks_data)
  stocks_data$SMI <- mySMI(stocks_data)
  stocks_data$ADX <- myADX(stocks_data)
  stocks_data$Aroon <- myAroon(stocks_data)
  stocks_data$BB <- myBB(stocks_data)
  stocks_data$ChaikinVol <- myChaikinVol(stocks_data)
  stocks_data$CLV <- myCLV(stocks_data)
  # stocks_data$EMV <- myEMV(stocks_data)
  stocks_data$MACD <- myMACD(stocks_data)
  stocks_data$MFI <- myMFI(stocks_data)
  stocks_data$SAR <- mySAR(stocks_data)
  stocks_data$Volat <- myVolat(stocks_data)

  ichimoku_dt = ichimoku(stocks_data2)
  stocks_data <- cbind(stocks_data,ichimoku_dt)
  # View(stocks_data)
  stocks_data <- data.frame(Date = index(stocks_data), coredata(stocks_data) )

  colnames(stocks_data) <- c("Date","Open","High","Low","Close","Volume","Adjusted","turningLine","baseLine","ATR","SMI","ADX","Aroon","BB","ChaikinVol","CLV","MACD","MFI","SAR","Volat")

  # logistic_stock_data <- stocks_data

  stocks_data$avg_price <- round((stocks_data$Open + stocks_data$Close)/2,2)

  # stocks_data <- mutate(stocks_data, next_day_close = lead(Close),next_day_open = lead(Open))
  # stocks_data$next_day_avg_price <- round((stocks_data$next_day_open + stocks_data$next_day_close)/2,2)

  # head(stocks_data)

  xbt <- stocks_data %>%
    select(Date, Open, High, Low, Close, Volume,Adjusted,avg_price,turningLine,baseLine,ATR,SMI,ADX,Aroon,BB,ChaikinVol,CLV,MACD,MFI,SAR,Volat) %>%
    # select(Date, Open, High, Low, Close, Volume,Adjusted,avg_price) %>%
    # select(Date, Open, High, Low, Close, Volume,Adjusted,avg_price,next_day_avg_price,turningLine,baseLine) %>%
    mutate(
      rsi = TTR::RSI(Close, 14),
      ema_10 = TTR::EMA(Close, 10),
      sma_10 = TTR::SMA(Close,10),
      ema_20 = TTR::EMA(Close,20),
      sma_20 = TTR::SMA(Close,20),
      ema_30 = TTR::EMA(Close, 30),
      sma_30 = TTR::SMA(Close,30),
      ema_50 = TTR::EMA(Close,50),
      sma_50 = TTR::SMA(Close,50),
      ema_100 = TTR::EMA(Close, 100),
      sma_100 = TTR::SMA(Close,100),
      ema_200 = TTR::EMA(Close,200),
      sma_200 = TTR::SMA(Close,200),
      VWMA_20 = TTR::VWMA(Close,Volume,n=20),
      HMA_9 = TTR::HMA(Close,n=9)
    )
  xbt <- as.data.frame(xbt)

  xbt <- na.omit(xbt)

  xbt = select(xbt,-c("Low","Open","High","Date","Adjusted"))

  logistic_stock_data <- xbt

  logistic_stock_data <- as.data.frame(logistic_stock_data)
  logistic_stock_data = select(logistic_stock_data,-c("avg_price"))

  logistic_stock_data$direction <- 0

  logistic_stock_data$direction <- ifelse(logistic_stock_data$Close > lead(logistic_stock_data$Close,1),1,0)
  # logistic_stock_data$direction <- ifelse(logistic_stock_data$Close > Lag(logistic_stock_data$Close,1),1,0)

  test_data_frame <- tail(logistic_stock_data,1)

  logistic_stock_data <- logistic_stock_data[which(!is.na(logistic_stock_data$direction)),]
  logistic_stock_data <- na.omit(logistic_stock_data)

  result <- logistic_stock_data[-1]
  row.names(result) <- logistic_stock_data$Date
  logistic_stock_data <- result

  set.seed(3456)

  # dt = sort(sample(nrow(logistic_stock_data), nrow(logistic_stock_data)*.7))
  #
  # train <- logistic_stock_data[dt,]
  # test <- logistic_stock_data[-dt,]
  #
  formula<- paste("direction ~ .",sep="")
  #
  #
  # model <- glm(formula,family="binomial",train)

  logistic_stock_data <- logistic_stock_data[!is.infinite(rowSums(logistic_stock_data)),]

  log_model <- glm(formula,family="binomial",logistic_stock_data)

  logistic_imp <- varImp(log_model, scale = FALSE)

  logistic_imp <- as.data.frame(logistic_imp)

  logistic_imp <- arrange(logistic_imp,desc(Overall))

  logistic_imp <- cbind(Variable = rownames(logistic_imp), logistic_imp)
  rownames(logistic_imp) <- 1:nrow(logistic_imp)

  # logistic_imp$Overall <- round(logistic_imp$Overall,2)
  # browser()

  logistic_imp = mutate(logistic_imp,
                        Overall_pct = round(Overall / sum(Overall) *100,2))


  final_importance <- logistic_imp %>% select(c("Variable","Overall_pct"))

  imp_variables <- head(final_importance,10)$Variable

  final_stocks_data <- logistic_stock_data %>% select(c(paste(imp_variables),"direction"))

  log_model <- glm(formula,family="binomial",final_stocks_data)

  # test_data <- tail(final_stocks_data,1)
  # pred <- predict(log_model,newdata = test_data,type = "response")

  test_data_frame <- tail(final_stocks_data,1) %>% select(c(paste(imp_variables),"direction"))

  print(test_data_frame)

  pred <- predict(log_model,newdata = test_data_frame,type = "response")


  pred_direction <- ifelse(pred > 0.5,"Buy","Sell")

  print(pred_direction)

  logistic_prediction[i,"Stock"] <- stock
  logistic_prediction[i,"Direction"] <- as.character(pred_direction)


}

# View(logistic_prediction)

colnames(logistic_prediction)

for (i in 1:nrow(logistic_prediction)) {
  stock = logistic_prediction[i,"Stock"]

  print(stock)

  Stock_df <- na.omit(getSymbols(stock, src = "yahoo", from = "2019-05-10", to = Sys.Date() , auto.assign = FALSE))

  Stock_df$Open = Stock_df[,1]
  Stock_df$High = Stock_df[,2]
  Stock_df$Low = Stock_df[,3]
  Stock_df$Close = Stock_df[,4]
  Stock_df$Volume = Stock_df[,5]
  Stock_df$Adj = Stock_df[,6]
  # cat(colnames(Stock_df))
  # cat(ncol(Stock_df))
  # cat(knitr::knit_print(DT::datatable(Stock_df, width = "100%")))

  Stock_df <- Stock_df[,c(7,8,9,10,11,12)]

  Stock_df <- data.frame(Date = index(Stock_df), coredata(Stock_df) )

  # print(tail(Stock_df,5))

  # Stock_df$v7_MA = ma(Stock_df$Close, order=7)
  # Stock_df$v30_MA <- ma(Stock_df$Close, order=30)

  rental_ma <- ts(na.omit(Stock_df$Close), frequency=30)
  decomp_rental <- stl(rental_ma, s.window="periodic")
  #plot(decomp_rental)
  adj_rental <- seasadj(decomp_rental)

  fit_s<-auto.arima(adj_rental, seasonal=TRUE)
  fcast <- forecast(fit_s, h=10)

  df <- fortify(fcast)

  # print(df)

  temp_end_Date = as.Date(Sys.Date())

  temp_prediction_date <- temp_end_Date + 24

  date_range <- seq.Date(temp_end_Date, temp_prediction_date, 1)

  next_days <- date_range[!weekdays(date_range) %in% (c("Saturday", "Sunday")) ]

  next_days <- as.data.frame(next_days)

  next_days <- next_days[1:10,]

  original_dates <- Stock_df$Date

  original_dates <- as.data.frame(original_dates)
  next_days <- as.data.frame(next_days)

  names(original_dates) <- c("Date")
  names(next_days) <- c("Date")

  final_dates <- rbind(original_dates,next_days)

  df$Date <- as.Date(final_dates$Date)

  temp <- head(df[which(df$`Point Forecast`>0),],1)

  forecasted <- as.numeric(temp$`Point Forecast`)
  ci_low_80 <- as.numeric(temp$`Lo 80`)
  ci_high_80 <- as.numeric(temp$`Hi 80`)
  ci_low_95 <- as.numeric(temp$`Lo 95`)
  ci_high_95 <- as.numeric(temp$`Hi 95`)

  logistic_prediction[i,"forecasted"] <- round(forecasted,2)
  logistic_prediction[i,"ci_low_80"] <- round(ci_low_80,2)
  logistic_prediction[i,"ci_high_80"] <- round(ci_high_80,2)
  logistic_prediction[i,"ci_low_95"] <- round(ci_low_95,2)
  logistic_prediction[i,"ci_high_95"] <- round(ci_high_95,2)

  # cat("Forecasted values : Actual forecast - ",forecasted,", Confidence 80 - ",ci_low_80,",",ci_high_80," and "," Confidence 95 - ",ci_low_95,",",ci_high_95)

}

```

---
**Disclaimer :**
**Prediction of stock prices has been an important area of research for a long time and this is purely built for Education purpose !!**
---
\
**Stock price prediction** is an important issue in the financial world, as it contributes to the development of effective strategies for stock exchange transactions. An accurate prediction has the high possibility to yield high financial benefits and hedge against market risks. 


Prediction methodologies are mainly classified into 3 types :

1. Fundamental Analysis :
    * Fundamental analysis is the process of measuring a security's intrinsic value by evaluating all aspects of a business or market. It includes analyzing the company’s future profitability on the basis of Income Statements, Balance Sheets, Cash Flows, Economic Growth, etc.
    <!-- - a bullet point -->
    <!-- + still a bullet point -->
  
2. Technical Analysis :
    * Analysts and investors use data of market activity such as historical returns, OHLC(Open, High, Low, Close) and volume of trades to generate Buy/Sell Signals. The most used Technicals are available in any technical analysis software. These include 200-day moving average, relative strength index, moving average convergence divergence, Super Trend, VWAP, Fibonacci Retracement and candle stick price chart.
    * Below is the Nifty50 Stocks table that contains the Classical and Fibonacci Retracement points for the next day i.e., `r  next_working_day`\
```{r, echo = FALSE}

 datatable(final_technical_data,extensions = c('FixedColumns'),
                     options = list(scrollX = TRUE, pageLength=10,fixedColumns = list(leftColumns = 3)
                     ))
```
    <!--     * Now with a sub-list to our sub-list -->
    <!--         * still with a sub-list to our sub-list -->
    <!-- - a bullet point -->
    <!-- + still a bullet point -->
    
3. Machine Learning :
   * Using Machine Learning to predict the stock prices is the game changer. This is so popular because Machine Learning as a whole is discover the hidden patterns in the data.
   - Direction - We see the historical up and downs of stock and imagine there are patterns. Implemented the Logistic Regression model to classify whether the stock is going to be Bullish/Bearish next day.
   - Price Prediction - We predict the prices based on time series data using Auto Regressive Integrated Moving Average (ARIMA). The time series model provides us the Closing price and the upper and lower confidence intervals (80% and 95%) for the observed data.

Below are the predictions made by using Machine Learning.
```{r, echo = FALSE}

datatable(logistic_prediction,extensions = c('FixedColumns'),
                     options = list(scrollX = TRUE, pageLength=10,fixedColumns = list(leftColumns = 3)
                     )) %>% formatStyle(
                     'Direction',
                     backgroundColor = styleEqual(c("Buy", "Sell"), c('green', 'red'))
                   )
```


